Advanced Normalization Tools (ANTS)

### 2011-04-14 Documentation/Tex/ants.tex
ENH: a simple implementation of COMPCOR based on input ROIs = CompCorRestingStateConnectivity in ImageMath
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@829 fd2da0a4-d968-48df-9cb5-d8c496287cbf

>>>>

\subsection{Statistical Mapping with ANTS: rsfMRI}
We are developing methods within ANTs to enable rsfMRI processing.  
The current strategy is within an ImageMath function called
CompCorRestingStateConnectivity.   This function will use pre-labeled
regions of the rsfMRI image to estimate the impact of physiological
confounds on the rsfMRI signal.  We implement the following steps 
\begin{enumerate}
\item Define matrices ${\bf G} , {\bf C},  {\bf R}$ which cover the
  gray matter region of interest, the confound region of interest and
  the reference region against which to compare the gray matter. 
\item Perform PCA on the ${\bf C}$ matrix to get its first N (e.g. 5)
  eigenvectors.  Use ordinary least squares to factor the effect of
  these out from the matrices ${\bf G} ,  {\bf R}$.
\item Get the first and second principal eigenvector from ${\bf R}$,
  the reference region.  
\item Correlate these against ${\bf G}$ on a voxel-by-voxel basis. 
\end{enumerate}
This has not been validated yet except by performing the same analysis
on a test-retest dataset with anterior cingulate as the reference
region.  This highlighted the thalamus, posterior cingulate and
cerebellum as part of the default mode network in both test and retest data.
